\textls[-0]{\thetitle}

### 2023-03-21 coqimpl.tex
move a redundant mention of mutually inductive types

The \Lang implementation currently does not yet bring extensibility to Coq's full
facility for inductive types.
Mutually inductive types and parameterized inductive types are not yet extensible,
though indexed inductive types are supported and can be used to encode parameterized ones.
Partial recursors are automatically generated only for non-indexed inductive types.
The case studies in \cref{sec:casestudies} do not exercise these features.
We believe that they do not pose conceptual challenges and can be
addressed with more engineering effort of the same kind that went into \Lang.

@@

What seems to require more thought from a language-design perspective is the
restriction that recursion and induction (on extensible types) cannot be nested.
%and must be at the top level through the \lsti{FRecursion} and \lsti{FInduction}
%commands.
A possible solution is to make the plugin generate proof obligations for
nested pattern matches when the inductive types acquire new constructors.
%
Also limiting (and interesting for future research) is
that generated propositional equalities cannot be used by Coq to automatically
reduce terms to definitionally equal forms, which causes inconveniences for
developments using intrinsically typed syntax.

>>>>

The \Lang implementation currently does not yet bring extensibility to Coq's full
facility for inductive types.
Mutually inductive types and parameterized inductive types are not yet extensible,
though indexed inductive types are supported and can be used to encode parameterized ones.
Partial recursors are automatically generated only for non-indexed inductive types.
These features are not exercised by our case studies (\cref{sec:casestudies})
but may be useful for modeling other languages.
We believe that they do not pose conceptual challenges and can be
addressed with more engineering effort of the same kind that went into \Lang.

@@

What seems to require more thought from a language-design perspective is the
restriction that recursion and induction (on extensible types) cannot be nested.
%and must be at the top level through the \lsti{FRecursion} and \lsti{FInduction}
%commands.
A possible solution is to make the plugin generate proof obligations for
nested pattern matches when the inductive types acquire new constructors.
%
Also limiting---and interesting for future research---is
that generated propositional equalities cannot be used by Coq to automatically
reduce terms to definitionally equal forms, which causes inconveniences for
developments using intrinsically typed syntax.
